---
title: "Confluence Scanner"
author: "Riley"
date: "11/16/2019"
output: html_document
---

Project Overview:

for a specified stock in the S&P 500 this code determines if the stock should be bought or sold based on the confluence of the SAR, Bollinger Band and RSI technical indicators. There are also divergence buy signals for when the price and RSI values are diverging (these are less accurate than the confluence signals).

Useful links on technical indicators used 
- Billinger Bands: https://www.investopedia.com/articles/technical/102201.asp
- Relative Strength Index (RSI): https://www.investopedia.com/terms/r/rsi.asp
- Parabolic Sar: https://www.investopedia.com/trading/introduction-to-parabolic-sar/
- Confluence trading: https://www.investopedia.com/terms/c/confluence.asp


Additional links on other mainstream technical indicators
- MACD (for trend or divergence indicators): https://www.investopedia.com/terms/m/macd.asp
- Stochastic Oscillator (momentum): https://www.investopedia.com/terms/s/stochasticoscillator.asp




Goal:
- Identify a set of indicators, that when used together (confluence) generate inter-day buy/sell signals that outperforms the market.
- Create a weight system so buy/sell signals can have higher/lower weights to help identify which signals are 'safer' trades (i.e greater divergence). Ideally this weight system can also identify which current ETFs owned should be traded to free up capital to buy a new 'safer' trade (i.e. the algorithm should be able to tell a user that a currently owned stock's momentum is slowing, or that they may be reaching a peak and they should sell that stock and buy a newly identified stock)



```{r}
if (!require(devtools)) install.packages('devtools')
library(BatchGetSymbols)
library(TTR)
library(zoo)
```


Download Data from Quandl
```{r}
first.date = Sys.Date() - 500
last.date = Sys.Date()

#Get tickers fro S&P500  list
SP500 = GetSP500Stocks()
tickers = SP500[,1]

# limit the number of tickers analyzed to random sample of 30
tickers = append(sample(tickers)[1:10], c('AAPL', 'AMZN', 'TSLA', 'GOOG', 'MSFT', 'HD')) #get a sample list of tickers to test with

#query data
DATA_query = BatchGetSymbols(tickers = tickers,
                             first.date = first.date,
                             last.date = last.date,
                             cache.folder = file.path(tempdir(),'BGS_Cache') )


x = nrow(DATA_query[[1]]) # define number of stocks analyzing

# get succesful ticker list from DATA_query[[1]] == 'keep'
S = matrix(data = NA, ncol = 1, nrow = x)
for(i in 1:x){
  if(DATA_query[[1]][i,6] == 'KEEP'){
    S[i] = toString(DATA_query[[1]][i,1])
  }
}
S = S[which(!is.na(S))] # remove NAs
x = length(S)
start_date = matrix(data = NA, ncol = x, nrow = 1)

DATA = list() #aggregate data into lists
for(i in 1:x){
  DATA[[i]] = DATA_query[[2]][which(DATA_query[[2]][,8] == S[i]),c(1:4,7)]
  if(DATA[[i]][nrow(DATA[[i]])-1,5] == DATA[[i]][nrow(DATA[[i]]),5]){
    DATA[[i]] = DATA[[i]][1:(nrow(DATA[[i]])-1),]
    print('Duplicate last date')
  }
  if(any(is.na(DATA[[i]]))){  # NAs = mean of t +/- 1
    na = which(is.na(DATA[[i]]), arr.ind = TRUE) # get NA locations (row, column)
    for(j in 1:nrow(na)){
      DATA[[i]][na[j,1], na[j,2]] = mean(c(DATA[[i]][na[j,1]-1, na[j,2]], DATA[[i]][na[j,1]+1, na[j,2]]))
    }
  }
  start_date[i] = DATA[[i]][1,5]
}
names(DATA) = S # name each df in list
# Unify lenghts -> have all matrices start at most recent start date
for(i in 1:x){
  if(start_date[i] != max(start_date)){
    DATA[[i]] = DATA[[i]][-1,]
  }
}

# Get list of successfule tickers to reference for testing
tickers = names(DATA) 
```


Analyze data
```{r}


#specify an ETF to analyze
j = 12
n_etf = j

# get data of single ETF
df = DATA[[n_etf]]
etf_name = tickers[n_etf]

# SMA Cross
long = 50
short = 20
sma_long = na.omit(SMA(df$price.close, long))
sma_short = na.omit(SMA(df$price.close, short))
  
  
# MACD
macd = na.omit(MACD(df$price.close, nFast = 12, nSlow = 26, nSig = 9, percent = TRUE))


#RSI Bands
rsi = na.omit(RSI(df$price.close, n = 14))
rsi_sd = rollapply(rsi, 20, sd, na.rm = TRUE) # caluclate standard deviation
rsi_mean = rollapply(rsi, 20, mean, na.rm = TRUE) # calc mean for rsi
rsi = rsi[(length(rsi) - length(rsi_sd) + 1):length(rsi)] # shorten rsi to match sd and mean length
rsi_lower = rsi_mean - 1.8*rsi_sd # calc lower rsi band
rsi_upper = rsi_mean + 1.8*rsi_sd # calc upper rsi band
rsi = cbind(rsi, rsi_mean, rsi_upper, rsi_lower)
  
# Stochastic RSI
stoch_rsi = na.omit(stoch(rsi[,1], nFastK = 14, nFastD = 3, sSlowD = 3, bounded = TRUE, smooth = 1))

  
# Donchian
donchian = na.omit(DonchianChannel(df[, 2:3], n = 10, include.lag = FALSE))
  
#BBands
bbands = na.omit(BBands(df[,2:4], n = 20))
bbands_1sd= na.omit(BBands(df[,2:4], n = 20, sd = 1))
  
#ADX
adx = na.omit(ADX(df[,2:4], n = 14))

#SAR
sar = SAR(df[,2:3])
  
# standardize length of data
new_length = min(length(sma_long),
                 length(sma_short),
                 length(macd[,1]),
                 length(rsi[,1]),
                 length(stoch_rsi[,1]),
                 length(donchian[,1]),
                 length(bbands[,1]),
                 length(bbands_1sd[,1]),
                 length(adx[,1]),
                 length(sar))

df = df[(nrow(df) - new_length + 1):nrow(df),]
sma_long = sma_long[(length(sma_long) - new_length + 1):length(sma_long)]
sma_short = sma_short[(length(sma_short) - new_length + 1):length(sma_short)]
macd = macd[(nrow(macd) - new_length + 1):nrow(macd),]
rsi = rsi[(nrow(rsi) - new_length + 1):nrow(rsi),]
stoch_rsi = stoch_rsi[(nrow(stoch_rsi) - new_length + 1):nrow(stoch_rsi),]
donchian = donchian[(nrow(donchian) - new_length + 1):nrow(donchian),]
bbands = bbands[(nrow(bbands) - new_length + 1):nrow(bbands),]
bbands_1sd = bbands_1sd[(nrow(bbands_1sd) - new_length + 1):nrow(bbands_1sd),]
adx = adx[(nrow(adx) - new_length + 1): nrow(adx),]
sar = sar[(nrow(sar) - new_length + 1): nrow(sar)]

rsi_volatility = rsi[,3] - rsi[,4] # doesn't need to be standardized because RSi is the same range for all ETFs
#standardize bb volatility
bb = bbands[,3] - bbands[,1]
bb_mean = mean(bb)
bb_sd = sd(bb)

BB_volatility = (bb-bb_mean)/bb_sd

# RSI and price 20-day mean delta
rsi_delta = as.vector(rsi[,1]*0)  #create empty vector
price_delta = as.vector(sma_short*0) # create empty price vector
price_rsi_div = as.vector(sma_short*0) # crete empty vector to fill with 1 and 0 if RSi and Price delta disagree or disagree

for(i in 2:length(rsi_delta)){
  
  # final - initial
  rsi_delta[i-1] = rsi[i,2] - rsi[i-1,2]
  price_delta[i-1] = sma_short[i] - sma_short[i-1]

  # check if price and rsi delta agree or *
  if(rsi_delta[i-1] > 0 & price_delta[i-1] > 0 | rsi_delta[i-1] < 0 & price_delta[i-1] < 0){
    
    price_rsi_div[i-1] = 0
    
  } else {
    
    price_rsi_div[i-1] = 1
  }
}


# Scale vectors so they can be merged
rsi_delta = scale(rsi_delta)
price_delta = scale(price_delta)


# calculate the weighted moving average
wma_divergence = WMA(price_rsi_div, n = 15, wts = 1:15)
wma_divergence[is.na(wma_divergence)] = 0 # replace NAs with 0

rsi_div_signal = .35 # if divergence score is greater than .2 then categorize it as a divergence
rsi_div_trade = which(wma_divergence > rsi_div_signal)



##Overbought/Oversold warnings
n = nrow(df)
rsi_buy = 0
rsi_sell = 0
bb_buy = 0
bb_sell = 0


# strategy:
# trade off the SAR indicator after a RSI trend reversal signal (30 & 75)

rsi_upper = 75
rsi_lower = 30
rsi_trigger = 0 
sar_buy = 0
sar_sell = 0


rsi_div_trigger = 0
rsi_div_buy = 0
rsi_div_sell = 0
bb_div_buy = 0
bb_div_sell = 0


for(i in 2:new_length){
  
  
  # set RSI trigger
  
  if(rsi[i,1] > rsi_upper){
    
    rsi_trigger = -1 # set signal to -1 to signal the SAR short @ next signal

  } else if (rsi[i,1] < rsi_lower){
    
    rsi_trigger = 1
  }
  
  
  # produce SAR trade signals
  
  if(df[i-1,4] < sar[i-1] & df[i,4] > sar[i] & rsi_trigger == 1){
    
    sar_buy = c(sar_buy,i)
    rsi_trigger = 0 # set the trigger back to 0
  
  
  } else if (df[i-1,4] > sar[i-1] & df[i,4] < sar[i] & rsi_trigger == -1){
    
    sar_sell = c(sar_sell,i)
    rsi_trigger = 0 # set the trigger back to 0
  }
  
  
  # Create BB and RSI Band trades during RSI divergence periods
  
  if(i %in% rsi_div_trade & df[i-1,4] < bbands[i-1,1] & df[i,4] > bbands[i,1]){
    
    # bb div buy
    bb_div_buy = c(bb_div_buy, i)
    
  } else if (i %in% rsi_div_trade & df[i-1,4] > bbands[i-1,3] & df[i,4] < bbands[i,3]){
    
    # bb div sell
    bb_div_sell = c(bb_div_sell, i)
    
    
  } else if (i %in% rsi_div_trade & rsi[i-1,1] < rsi[i-1,4] & rsi[i,1] > rsi[i,4]){
    
    # rsi div buy
    rsi_div_buy = c(rsi_div_buy, i)
    
  } else if (i %in% rsi_div_trade & rsi[i-1,1] > rsi[i-1,3] & rsi[i,1] < rsi[i,3]){
    
    # rsi div sell
    rsi_div_sell = c(rsi_div_sell, i)
    
  
  }
  
  
}

# remove the first zero
sar_buy = sar_buy[2:length(sar_buy)]
sar_sell = sar_sell[2:length(sar_sell)]


# add indicator to test output
if(j == 16){
  rsi_div_buy = c(rsi_div_buy, nrow(df))
}

## Determine if trigger a trade

print(etf_name)

#generate graphs


# color key
rsi_div_buy_col = 'green'
rsi_div_sell_col = 'orangered'
bb_div_buy_col = 'green'
bb_div_sell_col = 'orangered'
bbands_col = 'deepskyblue'
sar_col = 'blue'
sar_buy_col = 'green'
sar_sell_col = 'red'
div_range_col = 'grey'

# Closing price with all signals
plot(x = 1:n,
     y = df[,4],
     type = 'l',
     main = paste(etf_name, "Close Price & SAR & Divergence RSI & BB", sep = ": "))
lines(x = 1:n, y = sar, col = sar_col , lty = 3)
lines(x = 1:n, y = bbands[,1], lty = 3, col= bbands_col)
lines(x = 1:n, y = bbands[,3], lty = 3, col = bbands_col)
lines(x = 1:n, y = bbands[,2], lty = 3, col = bbands_col)
abline(v = sar_buy, col = sar_buy_col, lty = 1)
abline(v = sar_sell, col = sar_sell_col, lty = 1)
abline(v = rsi_div_trade, lty = 3, col = div_range_col)
abline(v = rsi_div_buy, lty = 2, col = rsi_div_buy_col)
abline(v = rsi_div_sell, lty = 2, col = rsi_div_sell_col)
abline(v = bb_div_buy, lty = 2, col = bb_div_buy_col)
abline(v = bb_div_sell, lty = 2, col = bb_div_sell_col)

legend('topleft', 
       legend = c('SAR',
                  'BBands',
                  'SAR Buy',
                  'SAR Sell',
                  'Divergence Buy',
                  'Divergence Sell',
                  'Divergene Rage'
                  ),
       col = c(sar_col,
               bbands_col,
               sar_buy_col,
               sar_sell_col,
               bb_div_buy_col,
               bb_div_sell_col,
               div_range_col),
       lty = c(3,3,1,1,2,2,3),
       cex = .5)



# RSI w/ Bands
#Plot RSI
plot(x = 1:n,
     y = rsi[,1],
     type = 'l',
     main = paste(etf_name, "RSI", sep = ": "))
lines(x = 1:n, y = rsi[,2], lty = 2)
lines(x = 1:n, y = rsi[,3], lty = 2, col = 3)
lines(x = 1:n, y = rsi[,4], lty = 2, col = 2)





# RSI & Price Difference Score
plot(x = 1:n,
     y = wma_divergence,
     type = 'l',
     main = paste(etf_name, "RSI & Price Divergence Score", sep = ": "))
abline(v = rsi_div_trade, lty = 2, col = 'grey')



  
  






```
